---
title: "Covariate Adjustment of Expression Data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Adjust gene expression data by batch, sex, and RIN and analyze cell type surrogate proportion variables

The analysis for cell type surrogate proportion variables uses the CellCODE library(https://github.com/mchikina/CellCODE) based on Chikina, Zaslavsky, & Sealfon, (2015) Bioinformatics, 10, 1584-1591. Paper can be found here: https://academic.oup.com/bioinformatics/article/31/10/1584/177237. 

## Setup

```{r, warning=FALSE, message=FALSE}
# load libraries
library(here)
install.packages(here("code","CellCODE"), repos=NULL, type="source")
library(easypackages)
libraries("here","limma","CellCODE","readxl","WGCNA","Biobase")
options(stringsAsFactors = FALSE)
```

## Read in data
```{r, warning=FALSE, message=FALSE}
# load in superset of mircroarray raw gex data
raw_gex_data = "~/Dropbox/data/ucsd_ace_microarray_data/dataQuantile.rda"
load(raw_gex_data)

# read in subject pheno list to use
subs2use = read_excel(here("data","tidy","MASTER_labelData+subgrp_sameoldermri.xlsx"))
subs2use = subset(subs2use,subs2use$use_subs==1)

gex_subset = dataQuantile[,subs2use$exprColNames]

# grab expression data
edata = exprs(gex_subset)
fdata = fData(gex_subset)

# collapse rows
collapsed_data = collapseRows(edata, fdata$geneSymbol, rownames(edata))
exprData = collapsed_data$datETcollapsed
geneInfo = data.frame(collapsed_data$group2row)
colnames(geneInfo) = c("geneSymbol","PROBE_ID")
geneInfo$geneSymbol[geneInfo$geneSymbol=="1-Mar"] = "MARCH1"
geneInfo$geneSymbol[geneInfo$geneSymbol=="2-Mar"] = "MARCH2"
geneInfo$geneSymbol[geneInfo$geneSymbol=="3-Mar"] = "MARCH3"
geneInfo$geneSymbol[geneInfo$geneSymbol=="4-Mar"] = "MARCH4"
geneInfo$geneSymbol[geneInfo$geneSymbol=="5-Mar"] = "MARCH5"
geneInfo$geneSymbol[geneInfo$geneSymbol=="6-Mar"] = "MARCH6"
geneInfo$geneSymbol[geneInfo$geneSymbol=="7-Mar"] = "MARCH7"
geneInfo$geneSymbol[geneInfo$geneSymbol=="8-Mar"] = "MARCH8"
geneInfo$geneSymbol[geneInfo$geneSymbol=="9-Mar"] = "MARCH9"

# grab pheno data
final_pdata = subs2use
final_pdata$Dx = final_pdata$diagnosis_binary
final_pdata$Dx[final_pdata$Dx=="PDDNOS"] = "ASD"
final_pdata$Dx = factor(final_pdata$Dx)
final_pdata$sex = factor(final_pdata$sex)
final_pdata$RIN = as.numeric(final_pdata$Final_RIN)
final_pdata$RIN[is.na(final_pdata$RIN)] = mean(final_pdata$RIN,na.rm=TRUE)
labelData = final_pdata

save(exprData,geneInfo,labelData, file = "~/Dropbox/ACE_sMRI_GEX_PLS/reproAnalysis/data/tidy/exprData_allGEXMRIsubs.Rdata")
write.csv(exprData,file = "~/Dropbox/ACE_sMRI_GEX_PLS/reproAnalysis/data/tidy/exprData_allGEXMRIsubs.csv")
write.csv(geneInfo,file = "~/Dropbox/ACE_sMRI_GEX_PLS/reproAnalysis/data/tidy/geneInfo_allGEXMRIsubs.csv")
write.csv(labelData,file = "~/Dropbox/ACE_sMRI_GEX_PLS/reproAnalysis/data/tidy/labelData_allGEXMRIsubs.csv")


# load gene expression data, gene information, and labels
load(here("data","tidy","exprData_allGEXMRIsubs.Rdata"))

# chi-square test on batch vs subtype
res = chisq.test(table(labelData$batch,labelData$subgrp))
res

# construct model
cov_columns = c("batch2","batchWG6","sex","RIN")
full_model = model.matrix(~0+as.factor(Dx) + 
                            as.factor(batch) + 
                            as.factor(sex) + 
                            RIN, 
                          data=labelData)
colnames(full_model) = c("ASD", "TD",cov_columns)

# fit model ----------------------------------------------------------
fit = lmFit(exprData,full_model)

# remove batch, sex, and RIN
beta1 = fit$coefficients[, cov_columns, drop = FALSE]
beta1[is.na(beta1)] = 0
exprDataAdj = exprData - beta1 %*% t(full_model[,cov_columns])

# save adjusted expression data
save(exprDataAdj,geneInfo,labelData, 
     file = here("data","processed","exprDataAdj.Rdata"))
```

## Estimate surrogate proportion variables for leukocyte cell types

```{r, warning=FALSE, message=FALSE}
data("IRIS")

ref_data = exprDataAdj
rownames(ref_data) = geneInfo$geneSymbol

cellTypes2use = c("Neutrophil-Resting","CD4Tcell-N0",
                  "Monocyte-Day0", "Bcell-naïve","NKcell-control")
cellTypeNames = c("Neutrophil","Tcell", "Monocyte","Bcell", "NKcell")
irisTag = tagData(IRIS[,cellTypes2use], 
                  cutoff = 2, 
                  max = 50, 
                  ref = ref_data, 
                  ref.mean = F)
colnames(irisTag)= cellTypeNames

SPVs = getAllSPVs(data = ref_data, 
                  grp = labelData$subgrp,
                  dataTag = irisTag,
                  method = "mixed",
                  plot = TRUE)
```

## Test SPVs for group-difference

```{r, warning=FALSE, message=FALSE}
SPVs = data.frame(SPVs)
labelData$Neutrophil = SPVs$Neutrophil
labelData$Tcell = SPVs$Tcell
labelData$Monocyte = SPVs$Monocyte
labelData$Bcell = SPVs$Bcell
labelData$NKcell = SPVs$NKcell

cols2use = c("Fstat","pval")
aov_res = data.frame(matrix(nrow = length(cellTypeNames), 
                            ncol = length(cols2use)))
rownames(aov_res) = cellTypeNames
colnames(aov_res) = cols2use

for (i in 1:length(cellTypeNames)){
  form2use = as.formula(sprintf("%s ~ subgrp",cellTypeNames[i]))
  mod2use = lm(formula = form2use, data = labelData)
  res = anova(mod2use)
  aov_res[cellTypeNames[i],"Fstat"] = res["subgrp","F value"]
  aov_res[cellTypeNames[i],"pval"] = res["subgrp","Pr(>F)"]
}
aov_res
```
