---
title: "WGCNA Analyses"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Run WGCNA

## Setup and read in data
```{r, warning=FALSE, message=FALSE}
# Libraries
library(easypackages)
libraries("WGCNA","gplots","here","ggplot2")

# Allow multi-threading within WGCNA
allowWGCNAThreads()

options(stringsAsFactors = FALSE)

# WGCNA parameters
networkType = 'signed'     
tomType = 'signed'
corrType = 'bicor'
maxBlockSize = 30000
minModSize = 100
modMergeCutHeight = 0.20
deepSplit = 4

resultpath = here("WGCNAresults")
dir.create(resultpath)

# Read in data
load(here("data","processed","exprDataAdj.Rdata"))

datExpr = t(exprDataAdj)
datTraits = as.data.frame(labelData[,c("subgrp",
                                       "age",
                                       "sex",
                                       "batch",
                                       "RIN")])
rownames(datTraits) = labelData$exprColNames
datTraits$sex = as.numeric(factor(datTraits$sex))
datTraits$subgrp = as.numeric(factor(datTraits$subgrp))
datTraits$batch = as.numeric(factor(datTraits$batch))
```

## Choose soft-threshold power
```{r, warning=FALSE, message=FALSE}
powers = c(1:30)
if (corrType=="pearson"){
  corFnc2use = "cor"
}else if (corrType=="bicor"){
  corFnc2use = corrType
}
sft = pickSoftThreshold(datExpr, 
                        powerVector = powers, 
                        verbose = 5, 
                        networkType = networkType, 
                        corFnc = corrType)

makeSoftPowerPlot <- function(sft, powers, cex1 = 0.9){
  # Scale-free topology fit index as a function of the soft-thresholding power
  par(mfrow = c(1,2))
  plot(sft$fitIndices[,1], 
       -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
       xlab = "Soft Threshold (power)",
       ylab = "Scale Free Topology Model Fit,signed R^2",
       type = "n",
       main = paste("Scale independence"))
  text(sft$fitIndices[,1], 
       -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
       labels = powers,
       cex = cex1,
       col = "red")
  abline(h = 0.90, col = "red")
  ## Mean connectivity as a function of the soft-thresholding power
  plot(sft$fitIndices[,1], 
       sft$fitIndices[,5],
       xlab="Soft Threshold (power)",
       ylab="Mean Connectivity", 
       type="n",
       main = "Mean connectivity")
  text(sft$fitIndices[,1], 
       sft$fitIndices[,5], 
       labels=powers, 
       cex=cex1,
       col="red")
}

makeSoftPowerPlot(sft = sft, powers = powers)
```

## Run blockwiseModules

```{r, warning=FALSE, message=FALSE}
softPower = 16

## Run an automated network analysis
net3 = blockwiseModules(datExpr,
                         power = softPower,
                         deepSplit = deepSplit,
                         minModuleSize = minModSize,
                         mergeCutHeight = modMergeCutHeight, 
                         detectCutHeight = 0.9999,
                         corType = corrType,
                         networkType = networkType,
                         pamStage = FALSE,
                         pamRespectsDendro = TRUE,
                         verbose = 3,
                         saveTOMs = FALSE,
                         maxBlockSize = maxBlockSize, 
                         numericLabels = TRUE)

net3$moduleNumbers = net3$colors
net3$colors = labels2colors(net3$moduleNumbers)

moduleLabels = net3$moduleNumbers
moduleColors = net3$colors
modNum_tab = data.frame(table(moduleLabels))
modCol_tab = data.frame(table(moduleColors))
modColNum_tab = cbind(moduleLabels = modNum_tab$moduleLabels, 
                      modCol_tab[order(-modCol_tab$Freq),])
knitr::kable(modColNum_tab)

rownames(net3$MEs) = labelData$subjectId
tmp_MEs = net3$MEs
# rename columns in net3$MEs
for (i in 1:dim(tmp_MEs)[2]){
  tmp_mnum = substr(colnames(tmp_MEs)[i], 3, nchar(colnames(tmp_MEs)[i]))
  if (nchar(tmp_mnum)==1){
    new_mnum = sprintf("M0%s",tmp_mnum)
  } else if (nchar(tmp_mnum)==2){
    new_mnum = sprintf("M%s",tmp_mnum)
  }
  colnames(tmp_MEs)[i] = new_mnum
}
net3$MEs_colreordered = tmp_MEs[,sort(colnames(tmp_MEs))]
nums2use = 0:(dim(tmp_MEs)[2]-1)
for (i in 1:length(nums2use)){
  colnames(net3$MEs_colreordered)[i] = sprintf("M%d",nums2use[i])
}
if (sum(colnames(net3$MEs_colreordered)=="M0")>0){
  net3$MEs_colreordered = net3$MEs_colreordered[,2:ncol(net3$MEs_colreordered)]
}

# order rows by subgrp2 and then subjectId
new_label_data = labelData
new_label_data2 = new_label_data[order(new_label_data$subgrp,
                                       order(new_label_data$subjectId)),]
net3$MEs_colreordered = net3$MEs_colreordered[new_label_data2$subjectId,]

# rename columns in net3$MEs
for (i in 1:dim(net3$MEs)[2]){
  tmp_mnum = substr(colnames(net3$MEs)[i], 3, nchar(colnames(net3$MEs)[i]))
  new_mnum = sprintf("M%s",tmp_mnum)
  colnames(net3$MEs)[i] = new_mnum
}
```

## Make TOM plot
```{r, warning=FALSE, message=FALSE}
plotDendroAndColors(net3$dendrograms[[1]], 
                    net3$colors, "Dynamic Tree Cut",
                    dendroLabels = FALSE, 
                    hang = 0.03, 
                    addGuide = TRUE, 
                    guideHang = 0.05,
                    main = "Gene dendrogram and module colors")
```

## Make eigengene network plot
```{r, warning=FALSE, message=FALSE}
MEcorMat = data.frame(cor(net3$MEs))
MEcorMat = MEcorMat[!(names(MEcorMat) %in% "M0"), 
                    !(names(MEcorMat) %in% "M0")]

heatmap.2(as.matrix(MEcorMat),
          col = blueWhiteRed(50), 
          Rowv = TRUE, 
          trace = "none",
          cellnote= round(as.matrix(MEcorMat),digits = 2), 
          notecol = "black",
          notecex=0.5,
          density.info = "none", 
          key.xlab ="ME Correlation (r)")
```

## Write out results files
```{r, warning=FALSE, message=FALSE}
# write ME files
fname2write = here("WGCNAresults","module_eigengenes.csv")
write.csv(net3$MEs,file = fname2write)
write.table(net3$MEs_colreordered, 
            file = here("WGCNAresults","data4pls.txt"), 
            quote = FALSE, 
            row.names = FALSE, 
            sep="\t",
            col.names = FALSE)

# compute module membership and write out to file
kme_data = signedKME(datExpr = datExpr, datME = net3$MEs)
for (i in 1:dim(net3$MEs)[2]){
  colnames(kme_data)[i] = sprintf("kME.%s",colnames(net3$MEs)[i])
}
geneInfo2use = geneInfo[,c("PROBE_ID","geneSymbol")]

wgcna_res_data = cbind(geneInfo2use,
                       data.frame(moduleLabels, moduleColors),
                       kme_data)
write.csv(wgcna_res_data, 
          file = here("WGCNAresults", "wgcna_results_summary.csv"), 
          quote = FALSE, 
          col.names = FALSE, 
          row.names = FALSE)
```

## Run DE analysis on module eigengenes

```{r, warning=FALSE, message=FALSE}
medata = net3$MEs
nmods = dim(medata)[2]
medata$group = factor(labelData$subgrp)
medata$sex = factor(labelData$sex)
medata$age = labelData$age
medata$Dx = factor(labelData$Dx)
medata$batch = factor(labelData$batch)
medata$RIN = labelData$RIN
covs2use = "group"

res_colnames = c("Module",
                 "Group.Fstat",
                 "Group.pval", 
                 "Group.fdr",
                 "TD_vs_ASDPoor.tstat",
                 "TD_vs_ASDPoor.pval",
                 "TD_vs_ASDPoor.fdr",
                 "TD_vs_ASDGood.tstat",
                 "TD_vs_ASDGood.pval",
                 "TD_vs_ASDGood.fdr",
                 "ASDGood_vs_ASDPoor.tstat",
                 "ASDGood_vs_ASDPoor.pval",
                 "ASDGood_vs_ASDPoor.fdr")
group_diff_res = data.frame(matrix(nrow = nmods-1, 
                                   ncol = length(res_colnames)))
colnames(group_diff_res) = res_colnames

for (imod in 1:(nmods-1)){
  module2use = sprintf("M%d",imod)
  group_diff_res$Module[imod] = module2use
  
  # test for subgroup effect
  form2use = as.formula(sprintf("%s ~ %s",module2use,covs2use))
  mod2use = lm(formula = form2use, data = medata)
  res = anova(mod2use)
  group_diff_res$Group.Fstat[imod] = res["group","F value"]
  group_diff_res$Group.pval[imod] = res["group","Pr(>F)"]

  # test for TD vs ASD Poor effect
  mask = medata$group=="TD" | medata$group=="Poor"
  tmp_data = subset(medata, mask)
  form2use = as.formula(sprintf("%s ~ %s",module2use,covs2use))
  mod2use = t.test(formula = form2use, data = tmp_data)
  group_diff_res$TD_vs_ASDPoor.tstat[imod] = mod2use$statistic
  group_diff_res$TD_vs_ASDPoor.pval[imod] = mod2use$p.value

  # test for TD vs ASD Good effect
  mask = medata$group=="TD" | medata$group=="Good"
  tmp_data = subset(medata, mask)
  form2use = as.formula(sprintf("%s ~ %s",module2use,covs2use))
  mod2use = t.test(formula = form2use, data = tmp_data)
  group_diff_res$TD_vs_ASDGood.tstat[imod] = mod2use$statistic
  group_diff_res$TD_vs_ASDGood.pval[imod] = mod2use$p.value
  
  # test for ASD Good vs ASD Poor effect
  mask = medata$group=="Good" | medata$group=="Poor"
  tmp_data = subset(medata, mask)
  form2use = as.formula(sprintf("%s ~ %s",module2use,covs2use))
  mod2use = t.test(formula = form2use, data = tmp_data)
  group_diff_res$ASDGood_vs_ASDPoor.tstat[imod] = mod2use$statistic
  group_diff_res$ASDGood_vs_ASDPoor.pval[imod] = mod2use$p.value
}#for (imod in 1:(nmods-1)){
rownames(group_diff_res) = group_diff_res$Module

# compute FDR
group_diff_res$Group.fdr = p.adjust(group_diff_res$Group.pval, 
                                    method = "fdr")
group_diff_res$TD_vs_ASDPoor.fdr = p.adjust(group_diff_res$TD_vs_ASDPoor.pval, 
                                            method = "fdr")
group_diff_res$TD_vs_ASDGood.fdr = p.adjust(group_diff_res$TD_vs_ASDGood.pval, 
                                            method = "fdr")
group_diff_res$ASDGood_vs_ASDPoor.fdr = p.adjust(group_diff_res$ASDGood_vs_ASDPoor.pval, 
                                                 method = "fdr")
group_diff_res
```

## Run WGCNA on TD only

```{r, warning=FALSE, message=FALSE}
# run on TD
grp2use = "TD"
datExpr_grp = datExpr[labelData$subgrp==grp2use,]
datTraits_grp = datTraits[labelData$subgrp==grp2use,]

# Choose a soft-threshold power
powers = c(1:30)
if (corrType=="pearson"){
  corFnc2use = "cor"
}else if (corrType=="bicor"){
  corFnc2use = corrType
}
sft = pickSoftThreshold(datExpr_grp, 
                        powerVector = powers, 
                        verbose = 5,
                        networkType = networkType,
                        corFnc = corrType)

makeSoftPowerPlot(sft = sft, powers = powers)

softPower = 16

## Run an automated network analysis
net_tmp = blockwiseModules(datExpr,
                            power = softPower,
                            deepSplit = deepSplit,
                            minModuleSize = minModSize,
                            mergeCutHeight = modMergeCutHeight, 
                            detectCutHeight = 0.9999,
                            corType = corrType,
                            networkType = networkType,
                            pamStage = FALSE,
                            pamRespectsDendro = TRUE,
                            verbose = 3,
                            saveTOMs = FALSE,
                            maxBlockSize = maxBlockSize, 
                            numericLabels = TRUE)

td_colors = labels2colors(net_tmp$colors)
datExpr_td = datExpr_grp
```

## Run WGCNA on ASD Good only

```{r, warning=FALSE, message=FALSE}
# run on ASD Good
grp2use = "Good"
datExpr_grp = datExpr[labelData$subgrp==grp2use,]
datTraits_grp = datTraits[labelData$subgrp==grp2use,]

# Choose a soft-threshold power
powers = c(1:30)
if (corrType=="pearson"){
  corFnc2use = "cor"
}else if (corrType=="bicor"){
  corFnc2use = corrType
}
sft = pickSoftThreshold(datExpr_grp, 
                         powerVector = powers, 
                         verbose = 5,
                         networkType = networkType,
                         corFnc = corrType)

makeSoftPowerPlot(sft = sft, powers = powers)

softPower = 16

## Run an automated network analysis
net_tmp = blockwiseModules(datExpr,
                            power = softPower,
                            deepSplit = deepSplit,
                            minModuleSize = minModSize,
                            mergeCutHeight = modMergeCutHeight,
                            detectCutHeight = 0.9999,
                            corType = corrType,
                            networkType = networkType,
                            pamStage = FALSE,
                            pamRespectsDendro = TRUE,
                            verbose = 3,
                            saveTOMs = FALSE,
                            maxBlockSize = maxBlockSize, 
                            numericLabels = TRUE)

asdgood_colors = labels2colors(net_tmp$colors)
datExpr_asdgood = datExpr_grp
```

## Run WGCNA on ASD Poor only

```{r, warning=FALSE, message=FALSE}
# run on ASD Poor
grp2use = "Poor"
datExpr_grp = datExpr[labelData$subgrp==grp2use,]
datTraits_grp = datTraits[labelData$subgrp==grp2use,]

# Choose a soft-threshold power
powers = c(1:30)
if (corrType=="pearson"){
  corFnc2use = "cor"
}else if (corrType=="bicor"){
  corFnc2use = corrType
}
sft = pickSoftThreshold(datExpr_grp, 
                        powerVector = powers, 
                        verbose = 5,
                        networkType = networkType,
                        corFnc = corrType)

makeSoftPowerPlot(sft = sft, powers = powers)

softPower = 16

## Run an automated network analysis
net_tmp = blockwiseModules(datExpr,
                            power = softPower,
                            deepSplit = deepSplit,
                            minModuleSize = minModSize,
                            mergeCutHeight = modMergeCutHeight,
                            detectCutHeight = 0.9999,
                            corType = corrType,
                            networkType = networkType,
                            pamStage = FALSE,
                            pamRespectsDendro = TRUE,
                            verbose = 3,
                            saveTOMs = FALSE,
                            maxBlockSize = maxBlockSize, 
                            numericLabels = TRUE)

asdpoor_colors = labels2colors(net_tmp$colors)
datExpr_asdpoor = datExpr_grp
```

## Function for reporting module preservation results

```{r, warning=FALSE, message=FALSE}
modulePreservationReport <- function(mp){
  ref = 1
  test = 2
  
  modColors = rownames(mp$preservation$observed[[ref]][[test]])
  moduleSizes = mp$preservation$Z[[ref]][[test]][, 1]
  plotMods = !(modColors %in% c("grey", "gold"))
  text = modColors[plotMods]
  plotData = cbind(mp$preservation$observed[[ref]][[test]][, 2], 
                   mp$preservation$Z[[ref]][[test]][, 2])
  mains = c("Preservation Median rank", "Preservation Zsummary")

  # Start the plot
  par(mfrow = c(1,2))
  par(mar = c(4.5,4.5,2.5,1))
  for (p in 1:2){
    min = min(plotData[, p], na.rm = TRUE)
    max = max(plotData[, p], na.rm = TRUE)
    # Adjust ploting ranges appropriately
    if (p==2){
      if (min > -max/10) min = -max/10
      ylim = c(min - 0.1 * (max-min), max + 0.1 * (max-min))
    } else
      ylim = c(max + 0.1 * (max-min), min - 0.1 * (max-min))
    plot(moduleSizes[plotMods], 
         plotData[plotMods, p], 
         col = 1, 
         bg = modColors[plotMods], 
         pch = 21,
         main = mains[p],
         cex = 2.4,
         ylab = mains[p], 
         xlab = "Module size", 
         log = "x",
         ylim = ylim,
         xlim = c(10, 2000), 
         cex.lab = 1.2, 
         cex.axis = 1.2, 
         cex.main =1.4)
    #labelPoints(moduleSizes[plotMods], 
    #            plotData[plotMods, p], 
    #            text, 
    #            cex = 1, 
    #            offs = 0.08);
    
    # For Zsummary, add threshold lines
    if (p==2) {
      abline(h=0)
      abline(h=2, col = "blue", lty = 2)
      abline(h=10, col = "darkgreen", lty = 2)
    } # if
  } # for
  
  statsObs = cbind(mp$quality$observed[[ref]][[test]][,-1], 
                   mp$preservation$observed[[ref]][[test]][,-1])
  statsZ = cbind(mp$quality$Z[[ref]][[test]][,-1], 
                 mp$preservation$Z[[ref]][[test]][,-1])
  
  sumTable = cbind(statsObs[, c("medianRank.pres", "medianRank.qual")],
               signif(statsZ[, c("Zsummary.pres", "Zsummary.qual")], 2))
  sumTable
} # function modulePreservationReport
```

## TD - ASD Good module preservation results

```{r, warning=FALSE, message=FALSE}
nperm = 1000
rand_seed = 1

setLabels = c("TD","ASDGood")
multiExpr = list(TD = list(data = datExpr_td), 
                 ASDGood = list(data = datExpr_asdgood))
multiColor = list(TD = td_colors)

mp_td_asdgood = modulePreservation(multiExpr,
                                   multiColor,
                                   networkType = networkType,
                                   corFnc = corFnc2use,
                                   referenceNetworks = 1,
                                   nPermutations = nperm,
                                   randomSeed = rand_seed,
                                   quickCor = 0,
                                   verbose = 0)

mp_res = modulePreservationReport(mp_td_asdgood)
mp_res
```

## TD - ASD Poor module preservation results

```{r, warning=FALSE, message=FALSE}
nperm = 1000
rand_seed = 1

setLabels = c("TD","ASDPoor");
multiExpr = list(TD = list(data = datExpr_td), 
                 ASDPoor = list(data = datExpr_asdpoor))
multiColor = list(TD = td_colors)

# Calculate module preservation stats
mp_td_asdpoor = modulePreservation(multiExpr,
                                   multiColor,
                                   networkType = networkType,
                                   corFnc = corFnc2use,
                                   referenceNetworks = 1,
                                   nPermutations = nperm,
                                   randomSeed = rand_seed,
                                   quickCor = 0,
                                   verbose = 0)

mp_res = modulePreservationReport(mp_td_asdpoor)
mp_res
```

## ASD Good - ASD Poor module preservation results

```{r, warning=FALSE, message=FALSE}
nperm = 1000
rand_seed = 1

setLabels = c("ASDGood","ASDPoor")
multiExpr = list(ASDGood = list(data = datExpr_asdgood), 
                 ASDPoor = list(data = datExpr_asdpoor))
multiColor = list(ASDGood = asdgood_colors)

# Calculate module preservation stats
mp_asdgood_asdpoor = modulePreservation(multiExpr,
                                        multiColor,
                                        networkType = networkType,
                                        corFnc = corFnc2use,
                                        referenceNetworks = 1,
                                        nPermutations = nperm,
                                        randomSeed = rand_seed,
                                        quickCor = 0,
                                        verbose = 0)

mp_res = modulePreservationReport(mp_asdgood_asdpoor)
mp_res
```